---
title: "analysis_3"
author: "Laura Christen"
date: '2022-07-22'
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
#set some global options
knitr::opts_chunk$set(echo=FALSE, warning = FALSE, message = FALSE)

#turn off scientific notation and round to 3 decimals
options(scipen=999, digits=3)

df <- read.csv("data.csv", fileEncoding="UTF-8-BOM", na.strings=c(""))

library(dplyr)
```

```{r}
#reverse code variables

df$emp8R <- 5-df$emp8

df$ref1R <- 5-df$ref1
df$ref3R <- 5-df$ref3
df$ref6R <- 5-df$ref6
df$ref8R <- 5-df$ref8
df$ref10R <- 5-df$ref10
df$ref12R <- 5-df$ref12
```

```{r}
df$empathy <- rowMeans(dplyr::select(df, emp1, emp2, emp3, emp4, emp5, emp6, emp7, emp8R, emp9, emp10, emp11, emp12, emp13, emp14, emp15, emp16))

df$refugees <- rowMeans(dplyr::select(df, ref1R, ref2, ref3R, ref4, ref5, ref6R, ref7, ref8R, ref9, ref10R, ref11, ref12R))

#hist(df$langprof, xlab='Language Proficiency')

df <- df %>% mutate(langprof = case_when(langprof == 10 ~ 'mono',
                                             langprof > 10 ~ 'biling'))

#df
df1 <- dplyr::select(df, langprof, refugees, empathy)

#df1
```

#Descriptive statistics by langprof group
```{r}
dplyr::group_by(df1, langprof) %>% 
  dplyr::summarise(Mean = mean(empathy, na.rm = T),
                 S.D. = sd(empathy, na.rm = T),
                 N = n()) %>% 
  flextable::flextable()

dplyr::group_by(df1, langprof) %>% 
  dplyr::summarise(Mean = mean(refugees, na.rm = T),
                 S.D. = sd(refugees, na.rm = T),
                 N = n())  %>% 
  flextable::flextable()
```


#demographic variables
```{r}
df2 <- dplyr::select(df, langprof, empathy, refugees, gender, age, education, work, religion, ethnic, politic, liveabroad, dist, ukraine)

df2<-subset(df2, gender!="Non-binary / third gender" & gender!="Prefer not to say" & work!="Prefer not to say" & religion!="Prefer not to say" & ethnic!="Prefer not to say" & education!="Other / prefer not to say")

#gender
df2$male <- ifelse(df2$gender == 'Male', 1, 0)


#education
df2 <- df2 %>% mutate(education = case_when(education == 'Primary education' ~ 'lower_ed',
                                            education == 'Upper secondary education (up to age 18)' ~ 'lower_ed',
                                            education == 'Lower secondary education (up to age 16)' ~ 'lower_ed',
                                            education == "Bachelor's degree or equivalent" ~ 'upper_ed',
                                            education == "Postgraduate or Master's degree or equivalent" ~ 'upper_ed'))

df2$upper_ed <- ifelse(df2$education == 'upper_ed', 1, 0)


#work status
df2 <- df2 %>% mutate(work = case_when(work == 'Unskilled/casual work (e.g., labourer, cleaner, fruit-picker)' ~ 'Work',
                                       work == 'Non-manual skilled (office-based employment; e.g., secretary, administrator, assistant manager)' ~ 'Work',
                                       work == 'Professional or managerial (e.g., lawyer, university teacher, company manager)' ~ 'Work',
                                       work == "Semi-skilled manual work (e.g., shop assistant, driver, waiter/waitress" ~ 'Work',
                                       work == "Skilled manual work (e.g., electrician, hairdresser, plumber)" ~ 'Work',
                                       work == 'Unskilled/casual work (e.g., labourer, cleaner, fruit-picker)' ~ 'Work', 
                                       work == 'Student' ~ 'Student',
                                       work == 'Retired' ~ 'Retired'
))

df2$Working <- ifelse(df2$work == 'Work', 1, 0)
df2$Retired <- ifelse(df2$work == 'Retired', 1, 0)


#religion
df2 <- df2 %>% mutate(religion = case_when(religion == 'Agnostic' ~ 'None',
religion == 'Christian (any denomination)' ~ 'Christian',                     
religion == 'Church of England' ~ 'Christian',                                        religion == "Hindu" ~ 'Other',
religion == "Jewish" ~ 'Other',
religion == 'Muslim (Sunni or Shia)' ~ 'Other',
religion == 'No religious affiliation' ~ 'None',                                       religion == 'Pagan' ~ 'Other',
religion == 'Pagan (Animist, see spirit in all things)' ~ 'Other',
religion == 'Spiritual' ~ 'Other',
religion == 'Other (please specify):' ~ 'Other'))

df2$Christian <- ifelse(df2$religion == 'Christian', 1, 0)
df2$OtherRel <- ifelse(df2$religion == 'Other', 1, 0)

#ethnicity
df2 <- df2 %>% mutate(ethnic = case_when(ethnic == 'White (including British, Irish, or any other White background)' ~ 'White',
                                       ethnic == 'Asian (e.g. Indian, Pakistani, Bangladeshi, Chinese)' ~ 'Other',
                                       ethnic == 'Black, African, Carribean, or Black British' ~ 'Other',
                                       ethnic == "Mixed or multiple ethnic backgrounds (e.g. White and Black Caribbean, White and Asian)" ~ 'Other',
                                       ethnic == "Other ethnic group" ~ 'Other'))


df2$NonWhite <- ifelse(df2$ethnic == 'Other', 1, 0)

#Ukrainian
df2$ukraine <- ifelse(df2$ukraine == 'Ukrainian', 1, 0)

#df2 <- na.omit(df2)
# df2

#Testing with just covariates
model1 <- lm(refugees ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age, df2)
summary(model1)

jtools::summ(model1, part.cor=T)$coeftable %>% 
  data.frame() %>% 
  round(3) %>% 
  dplyr::rename(B = Est.,
                t = t.val.,
                "Semipartial r" = part.r) %>% 
  dplyr::select(-c(partial.r)) %>% 
  tibble::rownames_to_column("Term") %>% 
  flextable::flextable()
```


#Now testing with predictor (the total effect)
```{r}
df2$Biling <- ifelse(df2$langprof == 'biling', 1, 0)

model2 <- lm(refugees ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + Biling, df2)
summary(model2)

jtools::summ(model2, part.cor=T)$coeftable %>% 
  data.frame() %>% 
  round(3) %>% 
  dplyr::rename(B = Est.,
                t = t.val.,
                "Semipartial r" = part.r) %>% 
  dplyr::select(-c(partial.r)) %>% 
  tibble::rownames_to_column("Term") %>% 
  flextable::flextable()
```

#Now testing with Ukraine
```{r}
modelq <- lm(refugees ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + ukraine + Biling, df2)
summary(modelq)

jtools::summ(modelq, part.cor=T)$coeftable %>% 
  data.frame() %>% 
  round(3) %>% 
  dplyr::rename(B = Est.,
                t = t.val.,
                "Semipartial r" = part.r) %>% 
  dplyr::select(-c(partial.r)) %>% 
  tibble::rownames_to_column("Term") %>% 
  flextable::flextable()
```


#HYPOTHESIS 1B
```{r}
model3 <- lm(empathy ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + Biling, df2)
summary(model3)

jtools::summ(model3, part.cor=T)$coeftable %>% 
  data.frame() %>% 
  round(3) %>% 
  dplyr::rename(B = Est.,
                t = t.val.,
                "Semipartial r" = part.r) %>% 
  dplyr::select(-c(partial.r)) %>% 
  tibble::rownames_to_column("Term") %>% 
  flextable::flextable()
```

#HYPOTHESIS 1C
```{r}
modele <- lm(refugees ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + empathy, df2)
summary(modelq)

jtools::summ(modele, part.cor=T)$coeftable %>% 
  data.frame() %>% 
  round(3) %>% 
  dplyr::rename(B = Est.,
                t = t.val.,
                "Semipartial r" = part.r) %>% 
  dplyr::select(-c(partial.r)) %>% 
  tibble::rownames_to_column("Term") %>% 
  flextable::flextable()
```

#HYPOTHESIS 2

#Testing both
```{r}
model4 <- lm(refugees ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + Biling + empathy, df2)
summary(model4)

jtools::summ(model4, part.cor=T)$coeftable %>% 
  data.frame() %>% 
  round(3) %>% 
  dplyr::rename(B = Est.,
                t = t.val.,
                "Semipartial r" = part.r) %>% 
  dplyr::select(-c(partial.r)) %>% 
  tibble::rownames_to_column("Term") %>% 
  flextable::flextable()
```
#The mediator (empathy) has a significant effect on the DV (refugees). The IV (Biling) is not individually a significant predictor


#mediation
```{r}
#install.packages("mediation")
library(mediation)

covList <- list("age", "male", "upper_ed", "Working", "Retired", "Christian", "NonWhite", "OtherRel")

results = mediate(model3, model4, treat = "Biling", mediator = "empathy", covariates = covList, boot=T)
summary(results)
```


#HYPOTHESIS 3
#Amongst those who speak another language, a longer amount of time spent abroad leads to higher levels of cognitive empathy, and therefore more positive perceptions of refugees.

#Testing the total effect
```{r}
df3 <- subset(df2, langprof == "biling")

model5 <- lm(refugees ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + liveabroad, df3)
summary(model5)
```

#Testing the mediator
```{r}
model6 <- lm(empathy ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + liveabroad, df3)
summary(model6)
```

#Testing both
```{r}
model7 <- lm(refugees ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + liveabroad + empathy, df3)
summary(model7)
```

#mediation
```{r}
results1 = mediate(model6, model7, treat = "liveabroad", mediator = "empathy", covariates = covList, boot=T)
summary(results1)
```


#HYPOTHESIS 4
#Amongst those who speak another language, the “further” the language is from English, the higher levels of cognitive empathy and therefore the more positive perceptions of refugees the participant will have.

#Testing the total effect
```{r}
model8 <- lm(refugees ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + dist, df3)
summary(model8)
```

#Testing the mediator
```{r}
model9 <- lm(empathy ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + dist, df3)
summary(model9)
```

#Testing both
```{r}
model10 <- lm(refugees ~ male + upper_ed + Working + Retired + Christian + NonWhite + OtherRel + age + dist + empathy, df3)
summary(model10)
```

#mediation
```{r}
results2 = mediate(model9, model10, treat = "dist", mediator = "empathy", covariates = covList, boot=T)
summary(results2)
```
